---
title: "Research Questions"
author: "Avner Peled"
date: "9/27/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggpubr)
library(tidyr)
library(reshape2)
```
```{r}
COLUMN_DICTIONARY <-
  c(
    Telerobot = "Q_GROUP_INTEREST_1",
    Telepuppet = "Q_GROUP_INTEREST_2",
    F2F = "Q_GROUP_INTEREST_3",
    Video = "Q_GROUP_INTEREST_4"
)
```


# Data outline

The following data is available for the survey participants.

## Demographics

 - **Age**: Continuous (1 year intervals, can be treated as continuous)
 - **Gender**: Nominal (Female/Male/Other).
 - **Tech confidence**: Ordinal (1-5).
 - **Spoken languages**: Nominal (checkboxes)
 - **Prior experience** - Dichotomous Y/N questions:
   1. Own a smartphone.
   2. Own a computer.
   3. Interacted with robots.
   4. Used glove puppets.
   5. Participated in intergroup encounters.
   6. Intergroup friends.


## General robot attitude

- **NARS Scale**: Continuous (lower is more positive attitude).
- **Feeling thermometer**: Continuous (higher is more positive).
- **Willingness to interact** - Ordinal 1-5s:
  1. _Approach_ a robot in a public space.
  2. _Own_ a robot used for interaction.
  3. _Operate_ a robot in a public space.
- **Imagine interaction**: Open text.

- **Interested to design a robot**: Dichotomous Y/N.

## Robot design preference

  - **What appearance** - Nominal: Human/animal or plant/machine/abstract/other
  - **How would it reflect me?** Dichotomous Y/N questions:
   1. Same nationality.
   2. Same age.
   3. Same gender.
   4. Same voice.
   5. Same religion.
   6. Additional objects.
   7. Not reveal anything.
   8. Be someone else.
   
 - **Features** - Ordinal 1-5s:
    1. Translate speech.
    2. Travel in space.
    3. Make hand gestures.
    4. Can tell when it is touched.
    5. Can show emotions.
    6. Can play content from the internet.
    7. Can show personal photos.
    8. Can play games.
    
  - **Other features** : Open text.
    
 - **Visiblity**: Nominal
   1. See and not be seee.
   2. See and be seen.
   3. Not see and not be seen.
   
## Robot puppet theater attitude
  - **Interested to perform**: Ordinal 1-5.
  - **What kind** : Open text.
  
## Attitude toward outgroup

- **Feeling thermometer**: Continuous (higher is more positive).
- - **Willingness to interact** - Ordinal 1-5s:
  1. _Operate_ a robot.
  2. _Perform_ a puppet.
  3. Face to face.
  4. Meet online.
  
## Robot preference when meeting outgroup

 - Duplicate of _Robot design preference_
 

# Research questions

## General attitude toward robots

## General attitude toward outgroup

## Interest in contact

### Q: How willing are the groups to meat each other with the different scenarios?
```{r}
 melt(Telerobot_ages %>% select(starts_with("Q_GROUP_INTEREST"), 'ResponseId','v') %>% drop_na() %>%     dplyr::rename(COLUMN_DICTIONARY), id=c('ResponseId','v'),variable.name = "INTEREST") %>% group_by(INTEREST) %>%
  get_summary_stats(value)
```

```{r}
  ggsummarystats(
  melt(Telerobot_ages %>% select(starts_with("Q_GROUP_INTEREST"), 'ResponseId','v') %>% drop_na() %>%     dplyr::rename(COLUMN_DICTIONARY), id=c('ResponseId','v'),variable.name = "INTEREST"),
  x = "INTEREST", y = "value",
  ggfunc = ggboxplot, palette="npg", add="mean", color="INTEREST",
  summaries = c("n", "median", "iqr", "mean"),
  digits = 3,
  table.font.size = 5,
  facet.by = "v"
)
```
