---
title: "Counts"
author: "Avner Peled"
date: "6/6/2021"
output:
  pdf_document: default
  html_document: default
---

```{r , include=FALSE}
library(dplyr)
library(haven)
knitr::opts_chunk$set(echo = TRUE)
```

# Basic counts

How many acccessed the survey from each side?

```{r}
 Telerobot_ages %>% count(v)
```

Male/female?
```{r}
 Telerobot_ages %>% count(Q_DEMOGRAPHICS_2) 
```

How many Finished the survey from each side?


```{r}
 Telerobot_ages %>% count(v, Finished)
```

```{r}
 Telerobot_ages %>% select(v,Q_TELEROBOT_IMAGINE) %>% drop_na() %>% count(v)
```

  How many on each side expressed willingness to meet the outgroup through a telerobot?
  According to the survey flow, Q_TELEROBOT_APP_G (robot apperance) is asked only if meeting the outgroup using a telerobot is higher than "Probably not"
  
```{r}
Telerobot_ages %>% 
  mutate(OUTGROUP_TELEROBOTS = !is.na(Q_TELEROBOT_APP_G)) %>%
  count(v, OUTGROUP_TELEROBOTS) %>%
  group_by(v) %>%
  mutate(freq = n / sum(n)) %>%
  ggplot(aes(x=OUTGROUP_TELEROBOTS, y=n, color=v)) + 
  geom_bar(stat="identity") + 
 # coord_polar("y", start=0) +
  facet_wrap(~ v) +   geom_text(aes(label = n, vjust = 1))
``` 
  Participated in an organized encounter?
  
```{r}
 Telerobot_sorted %>% count(v, Q_DEMOGRAPHICS_2_5)
```

Filter those out
```{r}
 Telerobot_no_conatct <- Telerobot_sorted %>% 
  filter(as_factor(Q_DEMOGRAPHICS_2_5) != "Yes" | is.na(Q_DEMOGRAPHICS_2_5))

 Telerobot_had_conatct <- Telerobot_sorted %>% 
  filter(as_factor(Q_DEMOGRAPHICS_2_5) == "Yes")
```



